Supporting Information

### 2018-03-30 SupportingInformation.Rmd
I think I got checkpoint to work

---
title: "Supporting Information"
author: "S. Ghosh, T. Loecke, C.P. Reid, Daniel Reuman"
date: "February 12, 2018"
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.8cm"

@@

<!--New latex commands-->
\newcommand{\mean}{\operatorname{mean}}
\newcommand{\var}{\operatorname{var}}
\newcommand{\cor}{\operatorname{cor}}
\newcommand{\Ps}{\operatorname{P}}
\newcommand{\Dsq}{\operatorname{D}^2}
\newcommand{\rank}{\operatorname{rank}}
<!--\newcommand{\D2}{\operatorname{D}^2} gives error msg : insert $ -->

<!--
```{r, echo=F}
options(knitr.table.format = "html")
```
-->

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
families<-c(1,3:10,13,14,16:20)

>>>>

---
title: "Supporting Information"
author: "S. Ghosh, T. Loecke, C.P. Reid, D.C. Reuman"
date: "February 12, 2018"
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.8cm"

@@

<!--New latex commands-->
\newcommand{\mean}{\operatorname{mean}}
\newcommand{\var}{\operatorname{var}}
\newcommand{\cor}{\operatorname{cor}}
\newcommand{\Ps}{\operatorname{P}}
\newcommand{\Dsq}{\operatorname{D}^2}
\newcommand{\rank}{\operatorname{rank}}

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
checkloc<-"./.checkpoint"
if (!dir.exists(checkloc))
{
  dir.create(checkloc)
  checkpoint("2018-03-29",checkpointLocation = checkloc)
}
```

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")

seed<-101
families<-c(1,3:10,13,14,16:20)
